% Software License Agreement
%
% Author    Robbie Edwards <redwards@clearpathrobotics.com>
% Copyright (c) 2016, Clearpath Robotics, Inc., All rights reserved.
%
% Redistribution and use in source and binary forms, with or without modification, is
% not permitted without the express permission of Clearpath Robotics.


\documentclass[]{clearpath-latex/clearpath-manual}
\graphicspath{{gen/}}
\usepackage{multirow}
\usepackage{gensymb}
\usepackage{dcolumn}
\usepackage{colortbl}
\usepackage{array}
\usepackage{needspace}



\begin{document}

\manualcover{maintenance-cover-page.pdf}
\tableofcontents

\section{Introduction}
This manual provides information and procedures for maintaining your Heron USVs

\subsection{Tools}

The recommended tools for working with your Heron USV are:

\begin{itemize}[nolistsep]
	\item Metric ball-head Allan Key set
	\item 0-120cNm Torque Driver with Phillips \#2 bit
	\item Phillips \#2 Screw driver
	\item Socket wrench with 1 in and 13/16 in sockets
	\item Metric wrench set
	\item Loctite - Red
\end{itemize}


\newpage

\section{Thruster Removal}

\section{Electronics Enclosure}

The user bay may be removed from the vehicle for maintenance or for shipment back to Clearpath Robotics. The following steps describe the removal and re-attachment process.

\section{Resetting PC BIOS}

Follow the steps in the Electronics Enclosure section to remove and open the enclosure. With the electronics enclosure open, plug a VGA monitor and keyboard into the PC. The robot may be powered with a battery or by plugging a 12V supply into the MCU's PWR input anderson connectors.

Power on the robot with the power button, press DEL while the PC is booting.

\section{Service and Support}
Clearpath is committed to your success with Heron. Please get in touch with us and we'll
do our best to get you rolling again quickly: \href{mailto:support@clearpathrobotics.com}{support@clearpathrobotics.com}
or visit out knowledge base for at \href{http://support.clearpathrobotics.com}{support.clearpathrobotics.com}

To get in touch with our sales team regarding Heron or other Clearpath Robotics products, please
email \href{mailto:sales@clearpathrobotics.com}{sales@clearpathrobotics.com}.

If you have a an issue that is specifically about ROS and is something which may be of interest
to the broader community, consider asking it on \href{http://answers.ros.org}{answers.ros.org}.
If you don't get a satisfactory response, please ping us and include a link to your question
as posted there. If appropriate, we'll answer in the ROS Answers context for the benefit of the
community.

\end{document}
